Paper_analyses

### 2021-09-02 Paper_Analyses_subj_obje_arousal.Rmd
Kmeans, finding K and visualising pca
a few lines to find the optimal k using the elbow method and to visualise the result because we have more than 2 variables the approach relies on pca projecting. A remaining problem has to do with what do do with repeated data within subject as the above was done on aggregated data

clustering_agg<- clustering_agg%>%
  mutate(Bio_Mean_HR_dif_z = scale(Bio_Mean_HR_dif, center  = TRUE, scale= TRUE))%>%
  mutate(pup_basCor_z = scale(pup_basCor, center  = TRUE, scale= TRUE))
  # mutate(BIO_CDA.PhasicMax_z = scale(BIO_CDA.PhasicMax, center  = TRUE, scale= TRUE))%>%
  #  mutate(BIO_CDA.ISCR_z = scale(BIO_CDA.ISCR, center  = TRUE, scale= TRUE))%>%
  # mutate(BIO_TTP.AmpSum_z = scale(BIO_TTP.AmpSum, center  = TRUE, scale= TRUE))%>%
  # mutate(BIO_CDA.SCR_z = scale(BIO_CDA.SCR, center  = TRUE, scale= TRUE))

@@

Kmeans random initialisation trap
- what happens if we have a bad ramdon inistialisation fior centroids (center of mass)?
The selection can ditacte the outcome.

@@

>>>>

clustering_agg<- clustering_agg%>%
  ungroup()%>%
  mutate(Bio_Mean_HR_dif_z = scale(Bio_Mean_HR_dif, center  = TRUE, scale= TRUE))%>%
  mutate(pup_basCor_z = scale(pup_basCor, center  = TRUE, scale= TRUE))
  # mutate(BIO_CDA.PhasicMax_z = scale(BIO_CDA.PhasicMax, center  = TRUE, scale= TRUE))%>%
  #  mutate(BIO_CDA.ISCR_z = scale(BIO_CDA.ISCR, center  = TRUE, scale= TRUE))%>%
  # mutate(BIO_TTP.AmpSum_z = scale(BIO_TTP.AmpSum, center  = TRUE, scale= TRUE))%>%
  # mutate(BIO_CDA.SCR_z = scale(BIO_CDA.SCR, center  = TRUE, scale= TRUE))

View(clustering_agg)

@@

Kmeans random initialisation trap
- what happens if we have a bad ramdon initialization fior centroids (center of mass)?
The selection can ditacte the outcome.

@@

note for clustering methods, because the solution is not known we don't typically have crossvalidation, but can asses stability, etc

regular k means on aggregaed data

```{r}
# K-Means Clustering

# Importing the dataset

clustering_agg<- subset(clustering_agg, !is.na(stimDescription))
colnames(clustering_agg)
clust_dataset = clustering_agg[c(20,24,25)]

# Feature Scaling
# training_set = scale(training_set)
# test_set = scale(test_set)

# Using the elbow method to find the optimal number of clusters
set.seed(6)
wcss = vector()
for (i in 1:10) wcss[i] = sum(kmeans(clust_dataset, i)$withinss)
plot(1:10,
     wcss,
     type = 'b',
     main = paste('The Elbow Method'),
     xlab = 'Number of clusters',
     ylab = 'WCSS')

# Fitting K-Means to the dataset
set.seed(29)
kmeans = kmeans(x = clust_dataset, centers = 3)
y_kmeans = kmeans$cluster

# Visualising the clusters
# install.packages("cluster")
library(cluster)

clusplot(clust_dataset,
         y_kmeans,
         lines = 0,
         shade = TRUE,
         color = TRUE,
         labels = 2,
         plotchar = FALSE,
         span = TRUE,
         main = paste('Clusters of customers'),
         xlab = 'Annual Income',
         ylab = 'Spending Score')

clustering_agg$y_kmeans<- y_kmeans

clustering_agg%>%
  ggplot(aes(as.factor(y_kmeans), ArousalMean))+
  geom_point()+
  stat_summary(geom = 'pointrange')

clustering_agg%>%
  ggplot(aes(as.factor(y_kmeans), ValenceMean))+
  geom_point()+
  stat_summary(geom = 'pointrange')

clustering_agg%>%
  ggplot(aes(as.factor(y_kmeans), valence))+
  geom_point()+
  stat_summary(geom = 'pointrange')

clustering_agg%>%
  ggplot(aes(as.factor(y_kmeans), arousal))+
  geom_point()+
  stat_summary(geom = 'pointrange')

?car::scatter3d
View(clustering_agg)
clustering_agg$y_kmeans<- as.factor(as.character(clustering_agg$y_kmeans))
car::scatter3d(clustering_agg$log_Bio_CDA.PhasicMax_z, 
          clustering_agg$Bio_Mean_HR_dif_z, 
          clustering_agg$pup_basCor_z,
          fit = "smooth",
          # point = FALSE,
          ellipsoid = TRUE,
          surface = FALSE,
          groups = clustering_agg$y_kmeans,
          point.col = clustering_agg$y_kmeans
          )

# install.packages("scatterplot3d") # Install
library("scatterplot3d") # load

scatterplot3d(clustering_agg[,c(20,24,25)],pch = 16, color = clustering_agg$y_kmeans, type="h")
text(clustering_agg$stimDescription, labels = clustering_agg$stimDescription,
     cex= 0.7, col = "steelblue")

require(ggplot2)
data("iris")

pca_res <- prcomp(clustering_agg[,c(20,24,25)], center = TRUE, scale. = TRUE)
plot_data <- cbind(as.data.frame(pca_res$x[, 1:2]), labels = clustering_agg$y_kmeans)

ggplot(plot_data, aes(x = PC1, y = PC2, colour = labels)) +
  geom_point()+
  geom_text(aes(label= clustering_agg$stimDescription))

summary(pca_res)
```
